Modern Graph Generators: A Survey

### 2018-09-16 challenges.tex
Minor corrections
Added privacy preserving in open challenges

\subsection{Simple Usage, simple Parameters}
The proposal of a data generator (not necessarily for graph data) has to face an
important schism. On one hand, it must provide the user with as
many parameters as possible in order to enable him/her to generate
arbitrary data.
This approach seems to be reasonable, but it entails a shortcoming due to
the fact that ordinary users are
unwilling to use complex benchmarking tools. This observation can be
seen, for example, in the case of XML benchmarks -- even though there exist
robust and complex data generators (such as
ToXGene~\cite{conf/webdb/BarbosaMKL02}, which supports specification of
structural aspects, value distributions, references etc.), the most popular
benchmarking tool is XMark~\cite{Schmidt:2002:XBX:1287369.1287455}, which models
a single use case and enables to specify just the size of the data. Hence, the
other extreme is to provide a simple data generator which does not require any
complex settings and thus guarantees a simple and fast benchmarking process.

@@

>>>>

\subsection{Simple Usage, Simple Parameters}
The proposal of a data generator (not necessarily for graph data) has to face an
important schism. On one hand, it must provide the user with as
many parameters as possible in order to enable him/her to generate
arbitrary data.
This approach seems to be reasonable, but it entails a shortcoming due to
the fact that ordinary users are
unwilling to use complex benchmarking tools. This observation can be
seen, for example, in the case of XML benchmarks -- even though there exist
robust and complex data generators (such as
ToXGene~\cite{conf/webdb/BarbosaMKL02}, which supports specification of
structural aspects, value distributions, references etc.), the most popular
benchmarking tool is XMark~\cite{Schmidt:2002:XBX:1287369.1287455}, which models
a single use case and enables to specify just the size of the data. Hence, the
other extreme is to provide a simple data generator which does not require any
complex settings and thus guarantees a simple and fast benchmarking process.

@@

\subsection{Privacy-preserving Graph Generation}

A lot of work have been conducted on the topic of privacy-preserving graph
randomization for publishing social graphs~\cite{wu2010survey}. However, very
little attention has been put on generating synthetic social graphs with
privacy-preserving guarantees.

Existing work focuses on generating graphs with ``differential
privacy''~\cite{dwork2009differential} guarantees. More specifically, in
~\cite{wang2013preserving} the authors develop a differential privacy graph
generation approach based on the dK-graph generation
model~\cite{mahadevan2006systematic} that outperforms the Stochastic Kronecker
Graph Model~\cite{LeskovecCKF05} in terms of the produced structural properties,
eventhough the results show that there is still room for improvement.

More on this line of research, recent work~\cite{qin2017generating} extends the notion of differential privacy
and propose an `` edge local differential privacy'' based graph generation
method. The poposed method allows generating privacy preserving synthetic social
graphs wihtout the need of a centralized data curator, while preserving structural
properties more accurately than than straw-hat methods such as Randomized
Neighbor Lists (based on randomized response~\cite{dwork2014algorithmic}) and
Degree-based Graph Generation (which perturbates the original graph degrees
using the Laplace mechanism~\cite{dwork2009differential}). Again, eventhough the
proposed technique outperforms the baselines, the results show that there is
still room for improvement.
